Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-03-20 src/tex/ms.tex
First comments added

%\definecolor{rb4}{HTML}{27408B}
%\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
%\newcommand{\kl}[1]{\color{cyan}[KL: #1 ]}
\newcommand{\ripple}{\texttt{ripple}}
\newcommand{\python}{\texttt{python}}
\newcommand{\jax}{\texttt{jax}}
\newcommand{\zdethp}{\texttt{zdethp}}

@@

% Main body with filler text
\section{Introduction} \label{sec:intro}

@@

% Waveform families and slight motivation of why we take Phenom model
Currently, three families of GW models are commonly used. They are the
effective-one-body (EOB) \citep{taracchini2014effective}, Numerical Relativity
(NR) surrogate \citep{varma2019surrogate} and phenomenological (Phenom) models
\citep{husa2016frequency,khan2016frequency} \kw{Add more citations related to
the newest models}. EOB models are constructed by mapping two masses onto an
effective body under an effective metric; NR surrogate models construct
waveforms using combinations of NR waveforms; Phenom models are formulated using
specific ansatz and inspiral approximations. While EOB and NR surrogate models
give better waveform approximants, Phenom waveforms can be produced much faster,
hence it is used mostly in data analysis tasks that requires many waveform
generations. This advantage scales up in data analysis tasks such as matched
filtering and parameter estimation, where many waveforms are required in each
run. This motivates us to improve upon the current framework of Phenom models,
thus can retain the advantage of fast waveform generation while improving the
model's accuracy.

@@

The rest of the paper is structured as follows: In Sec.~\ref{sec:method}, we
review the parameterization of the IMRPhenomD model and the mismatch function
that is used as an objective function for the calibration, followed by outlining the
specific optimization scheme used for recalibration. In
Sec.~\ref{sec:result}, we give the optimization result by comparing mismatches
of optimized waveforms with original waveforms. We also show how the
optimization result differs with waveforms of different intrinsic parameters. In
Sec.~\ref{sec:discussion}, we address the difference between our calibrating
procedure with \citep{khan2016frequency}. We also explain how reduced spin
parameterization affects the accuracy of the model.

@@

In order to recalibrate the model, we have to understand what parameters the model has.
Here we give a succinct summary of the IMRPhenomD model and the relevant parameters.
For interested readers, please refer to \cite{khan2016frequency} for more details on construction of the model.

The IMRPhenomD model is constructed by combining three individually fitted parts
into one coherent waveform model, which consists of the inspiral, intermediate, and merger-ringdown part, 
\kw{Check if the following equation is correct. I think it is off by some smoothing factors.}
\begin{align}
	h(f,\theta)&=h_{\mathrm{ins}}(f,\theta) + h_{\mathrm{int}}(f,\theta) + h_{\mathrm{me-rd}}(f,\theta).
\end{align}

Instead of fitting the strain, which is a highly oscillatory function that is
difficult to fit, the amplitude and phase are fitted since they are smoother
functions. In each part, the amplitude and phase are made using simple functions
of frequency such as polynomials or lorentzians. These simple analytic functions
consists of parameters $\Lambda^i$, which are defined as follows. \kw{Can you
change equation one such that it consists of $\Lambda$? Also be explicit about
the form of the function used for the fitting. Like write down the polynomials
and lorentizans for the specific parts.}
\begin{align} \label{eq:Lambda}
	\Lambda^i&=\lambda_{00}^i+\lambda_{10}^i\eta \nonumber \\
	&+(\chi_{\mathrm{PN}}-1)(\lambda_{01}^i+\lambda_{11}^i\eta+\lambda_{21}^i\eta^2) \nonumber \\ 
	&+(\chi_{\mathrm{PN}}-1)^2(\lambda_{02}^i+\lambda_{12}^i\eta+\lambda_{22}^i\eta^2) \nonumber \\
	&+(\chi_{\mathrm{PN}}-1)^3(\lambda_{03}^i+\lambda_{13}^i\eta+\lambda_{23}^i\eta^2),
\end{align}
where $\lambda$ are fitting coefficients obtained during calibration, $\eta$ is
the symmetric mass ratio, and $\chi_{\mathrm{PN}}$ is the post-Newtonian spin
parameter, which is defined as 
\begin{align}
	\chi_{\mathrm{PN}}=\frac{m_1\chi_1+m_2\chi_2}{m_1+m_2}-\frac{38\eta}{113}(\chi_1+\chi_2).
\end{align}
Here, $m_{1,2}$ and $\chi_{1,2}$ are the primary and secondary mass and spin,
respectively. Finally, the individual segments are connected in a way that the
final waveform is continuous in its first derivative \kw{expand a bit}.

\kw{Need to work on this paragraph}
From Eq. \ref{eq:Lambda}, we can see that the values of $\lambda$ are
fundamental to waveform generation, which can significantly affect the shape of
final waveforms. Thus, having a set of accurate waveform coefficients is
important. Generally, waveform coefficients are obtained by calibrating with NR
waveforms, which are waveforms computed using NR simulations. In the case of
\citep{khan2016frequency}, $\lambda$ were obtained by fitting model-generated
waveforms to NR waveforms. For each NR simulation, they can obtain one set of
$\Lambda$'s through optimization. With many sets of $\Lambda$, $\lambda$ are
subsequently found by fitting against Eq. \ref{eq:Lambda}. Since the fitting
procedure is done in a piece-wise manner, the correlations between different
segments are omitted, which could limit the accuracy of the model. Also,
their calibration procedure does not guarantee to have the optimal set of
$\lambda$, since the process of connecting segments alters the previously fitted
waveform. The model-generated waveforms do not take this effect into account,
and thus introduces additional inaccuracies.

@@

In the original calibration \citep{khan2016frequency,husa2016frequency},
training waveforms are hybrid waveforms of NR simulations and SpinAlignedEOB
(SEOB) waveforms. The low frequency inspiral part is taken from the SEOB
waveforms while the rest of the waveforms are taken from NR simulations.
Instead, we solely use NR waveforms for comparison, since most NR waveforms used
have long enough time series data, i.e.~$>15$ orbits \citep{boyle2019sxs}, in
which they are long enough to contain part of the inspiral segment and all
merger and ringdown frequency information. We take the frequency limits as
$f_{\mathrm{min}}=0.1f_{\mathrm{RD}}$ and $f_{\mathrm{max}}=1.2f_{\mathrm{RD}}$,
where $f_{\mathrm{RD}}$ is the frequency at ringdown. This range covers most of
the IMRPhenomD's frequency range, except the minimum frequency is set higher
than that in the original calibration due to NR length. When compared with
IMRPhenomC, the frequency range is slightly extended to have a higher maximum
frequency.

We choose to use two different noise spectra $S_n(f)$, namely the zero-detuned
high-power (\zdethp) noise spectrum and a constant spectrum. Since in any data
analysis tasks, model-generated waveforms will ultimately be used to compare
with GW observations, they are subjected to the sensitivity of detectors. Hence,
it is sensible to have waveforms calibrated with {\zdethp} spectrum rather than
a non-weighted spectrum. However, with sensitivity curve involved, we have to
choose a corresponding mass scale. Here, we simply choose $M=50M_{\odot}$ for
all waveforms, since this mass scale is common in LIGO observations. On the
other hand, we also recalibrated coefficients with the constant spectrum for a
more general purpose.

@@

% \kw{Mention the main advantage in this study is we can optimize everything at
% once.}

% To recalibrate the model, we have to define loss functions that quantify the
% difference between the model-generated waveforms and NR waveforms. In the
% original calibration, they took the mean square error as the loss function for
% optimization. Instead, we directly use mismatch as our metric for loss
% functions. However, the mismatch of individual waveforms is not useful in
% optimization, since it does not represent all waveforms with various intrinsic
% parameters. We ought to calibrate coefficients that suit waveforms with
% different intrinsic parameters simultaneously, hence waveforms in different
% regions of parameter space should be used in the optimization scheme. Here, we
% chose two different loss functions to examine their ability to optimize the
% model, e.g. mean of individual mismatches $\mathcal{L}_{\mathrm{mean}}$ and
% fractional loss $\mathcal{L}_{\mathrm{fl}}$.

@@

% To recalibrate the model, we need to define a loss function that quantify ...
% We use mismatch over the set of all training waveforms as the loss function.
% We choose mismatch as the loss function because it is closely related to
% downstream objectives such as the likelihood in parameter estimation. The
% mismatch is averaged over the training dataset to cover the parameter space of
% interest. (used)
\begin{align}
	\mathcal{L}_{\mathrm{mean}}&=\frac{1}{N}\sum_{i=1}^N\mathcal{M}_i \\
	\mathcal{L}_{\mathrm{fl}}&=\frac{1}{N}\sum_{i=1}^N\frac{\mathcal{M}_i}{\mathcal{M}_{i,\mathrm{ini}}},
\end{align}	
$\mathcal{M}_i$ represents the mismatch of an individual training waveform,
$\mathcal{M}_{i,\mathrm{ini}}$ represents the initial mismatch of the individual
training waveform, and $N$ is the total number of individual training waveforms.
For the first choice, it takes the mean of the mismatches, which serves as a
basic loss function. However, it is prone to be dominated by a single waveform
with a large mismatch. Other waveforms with smaller mismatches would be
insignificant comparatively, and might not be able to improve under such
optimization. Alternatively, the second choice, the mean of normalized
mismatches, eliminates the aforementioned issue. Nevertheless, it excludes the
information on initial mismatches. $\mathcal{L}_{\mathrm{fl}}$ restricts every
training waveform to decrease at similar rates, hence it is hard to obtain
optimized waveforms with mismatches in the same order of magnitude. Instead,
their ratios in mismatches would remain approximately the same. Conversely,
$\mathcal{L}_{\mathrm{mean}}$ allows the loss function to automatically adjust
and final individual mismatches would be in a similar order of magnitude. In
this paper, we display the results of using both loss functions and examine the
difference between them.

@@

@@

\begin{figure*}[t]
	\script{0154.py}
	\centering
	\includegraphics[width=\textwidth]{figures/0154.pdf}
	\caption{Comparison between original and optimized IMRPhenomD waveforms.
	Here shows the SXS:BBH:0154 NR waveform, which has mass ratio $q=1$ and
	$\chi_1=\chi_2=-0.8$. The original mismatch is around $2.8\times10^{-4}$ and
	the optimized mismatch is around $5.3\times10^{-5}$. Top: It shows the
	amplitude and phase of NR, original IMRPhenomD and optimized IMRPhenomD
	waveform. Bottom: It shows the relative error of amplitudes between NR and
	IMRPhenomD waveforms, and the absolute error of phases between NR and
	IMRPhenomD waveforms}
	\label{fig:0154}
\end{figure*}

@@

We first examine the effect of joint optimization on a single waveform. In
Fig.~\ref{fig:0154}, we can see that the optimized waveform has better accuracy
than the original waveform, especially in the inspiral region, where the
amplitude has a $50\%$ decrease in error. We have chosen one of the testing
waveforms listed in \citep{khan2016frequency} for a fair comparison. 
% In general, most waveforms within the neighborhood of the training waveforms
% show improvement in mismatches.

@@

% \kw{We then compute the mismatch for all testing waveforms and plot the
% distribution of the mismatch in figure X. We find the distribution...}

@@

% We believe that either the ansatz does not suit waveforms within certain
% regions of parameter space or the set of optimized coefficients falls to a
% minimum where they do not fit some testing waveforms. If in some region of
% parameter space, the ansatz does not fit well with NR waveforms, it would
% never be able to have consistent improvement under optimization. Instead, it
% would surf around the loss manifold with random fluctuations in mismatches. If
% the set of coefficients does not fit, then dividing the parameter space into
% regions and fitting separate sets of coefficients should give better results.

@@

Furthermore, we plot the parameter space of $\chi_1$ vs. $\chi_2$ in
Fig.~\ref{fig:ps_q148}. Waveforms along the diagonal axis, i.e.
$\chi_1\approx\chi_2$, show good mismatch improvements. We expect to see this
feature since the original coefficients were fitted using NR waveforms with
equal or similar spin, hence the model prefers waveforms with similar spin. One
interesting feature is how the second and fourth quadrants respond to
optimization. In the second quadrant ($\chi_1<0$ and $\chi_2>0$), waveforms
generally improve with along optimization. However, mismatches in the fourth
quadrant ($\chi_1>0$ and $\chi_2<0$) do not improve after optimization. Most
waveforms even turned worse after optimization. These waveforms correspond to
the waveforms in the high mismatch tail in Fig.~\ref{fig:q148}.

% Waveform mismatches in the fourth quadrant, i.e. $\chi_1>0$ and $\chi_2<0$,
% performed worse after optimized. IMRPhenomD is constructed using single spin
% parameter, where there are degeneracy between $\chi_1$ and $\chi_2$. In
% regions with opposite extreme spin components, degeneracy significantly alters
% intrinsic parameters passed into waveform generation, hence the fourth
% quadrant shows such feature.

\begin{figure}[t]
	\script{ps_q148_qchi.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/ps_q148_qchi.pdf}
	\caption{Parameter space of testing waveforms of
	$q$~vs.~$\chi_{\mathrm{PN}}$. We use the recalibrated result from
	$\mathcal{L}_{\mathrm{mean}}$ with the constant noise spectrum and training
	waveforms in Tab.~\ref{tab:q148}. Here, the colorbar represents the
	$\log_{10}$ difference between optimized and original unweighted
	mismatches.}
	\label{fig:ps_q148_qchi}
\end{figure}
\begin{figure}[t]
	\script{ps_q148_chi1chi2.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/ps_q148_chi1chi2.pdf}
	\caption{Parameter space of testing waveforms of $\chi_1$~vs.~$\chi_2$. We
	use the recalibrated result from $\mathcal{L}_{\mathrm{mean}}$ with the
	constant noise spectrum and training waveforms in Tab.~\ref{tab:q148}.}
	\label{fig:ps_q148}
\end{figure}

@@

\begin{figure}[t]
	\script{all_quadrants.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/all_quadrants.pdf}
	\caption{Distributions of mismatches after optimizing in separate quadrants.
	We use a constant noise spectrum to calculate mismatch and
	$\mathcal{L}_{\mathrm{mean}}$ for the loss function. Generally, most
	waveforms with mismatch $>10^{-2}$ lies in the fourth quadrant. }
	\label{fig:all_quadrants}
\end{figure}

@@

%\begin{enumerate} \item Comparison with the original paper is not the same.
%   (Different waveforms, different ways to modify the waveform, different range
%   of frequencies) \item More waveforms are taken so it should be more robust,
%   since the parameter space coverage is better. \item Problems with IMRPhenomD
%   model, i.e. $\chi_{\mathrm{eff}}$ reduces the dimension of spin space
%   $\chi_1, \chi_2$, so the model is flawed. Comparison issues. (Caveat) \item
%   Can in principle split parameter space into regions that can be separately
%   optimized. If not, then its must be the model's problem. Would the region
%   classification be made automatic. Are there any algorithms to do so? \item
%   Future work (Repeat on other GW models. Mapping between NR surrogate to see
%   any systematics.) \end{enumerate}

We have shown the result of recalibrating waveform coefficients. One thing to
note is that our recalibration procedure is not exactly the same as the original
calibration. For instance, we use a different set of NR waveforms, frequency
range, etc. Nonetheless, as the decrease in mismatch is rather significant, this
optimization procedure should be able to improve the accuracy of IMRPhenomD on a
similar scale regardless of the differences. Here, this result serves as a
demonstration of the general method used.  
% In Fig.~\ref{fig:0154}, the error in the inspiral region is around halved for
% both amplitude and phase. Similarly, for the merger-ringdown region, the
% optimized waveforms also show great improvement.

@@

% Can we further check systematic bias by injection? But how can we know the
% real mass or spin in the first place if we disregard GW models.

@@

% From analyzing mismatches in parameter space, we investigated the accuracy of
% generated waveforms based on their mass ratio and spin. Similar studies can be
% performed on other GW models to give better criteria to

% Improved the IMRPhenomD model. Found regions that can be improved. Checked
% ansatz.

>>>>

\definecolor{rr}{RGB}{173, 37, 37}
%\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
%\newcommand{\kl}[1]{\color{cyan}[KL: #1 ]}
\newcommand{\te}[1]{{\color{rr}[TE: #1 ]}}
\newcommand{\ripple}{\texttt{ripple}}
\newcommand{\python}{\texttt{python}}
\newcommand{\jax}{\texttt{jax}}
\newcommand{\zdethp}{\texttt{zdethp}}

@@

% Main body with filler text
\section{Introduction} \label{sec:intro}
\te{General points:}

@@

% Waveform families and slight motivation of why we take Phenom model
Currently, three families of GW models are commonly used. They are the effective-one-body (EOB) \citep{taracchini2014effective}, Numerical Relativity (NR) surrogate \citep{varma2019surrogate} and phenomenological (Phenom) models \citep{husa2016frequency,khan2016frequency}. EOB models are constructed by mapping two masses onto an effective body under an effective metric; NR surrogate models construct waveforms using combinations of NR waveforms; Phenom models are formulated using specific ansatz and inspiral approximations. While EOB and NR surrogate models give better waveform approximants, Phenom waveforms can be produced much faster, hence it is used mostly in data analysis tasks that requires many waveform generations. This advantage scales up in data analysis tasks such as matched filtering and parameter estimation, where many waveforms are required in each run. This motivates us to improve upon the current framework of Phenom models, thus can retain the advantage of fast waveform generation while improving the model's accuracy.

@@

The rest of the paper is structured as follows: In Sec.~\ref{subsec:waveform_model}, we explain how IMRPhenomD is constructed and have a detailed explanation of how waveform coefficients are introduced to the model. We discuss the mismatch in Sec.~\ref{subsec:mismatch}, where we explained how we calculate it in conjunction with NR waveforms. Then, we describe the optimization scheme used for recalibration in Sec.~\ref{subsec:optimization}. In Sec.~\ref{sec:result}, we give the optimization result by comparing mismatches of optimized waveforms with original waveforms. We also show how the optimization result differs with waveforms of different intrinsic parameters. In Sec.~\ref{sec:discussion}, we address the difference between our calibrating procedure with \citep{khan2016frequency}. We also explain how reduced spin parameterization affects the accuracy of the model.

@@

IMRPhenomD is a frequency-domain phenomenological model for modeling spin-aligned BBH coalescence events. It was developed as an overhaul of previous Phenom models, such as  IMRPhenomB/C \citep{santamaria2010matching,ajith2011inspiral}, to give higher accuracy for GW data analyses. 
% Using {\ripple} \citep{ripple} and {\jax} \citep{jax2018github}, we are able to easily recalibrate the model. 
IMRPhenomD is constructed in separate segments, i.e. inspiral, intermediate, and merger-ringdown. 
\begin{align}
	h(f,\theta)&=h_{\mathrm{ins}}(f,\theta) + h_{\mathrm{int}}(f,\theta) + h_{\mathrm{me-rd}}(f,\theta)
\end{align}
In each segment, the amplitude and phase are made using simple functions of frequency such as polynomials or lorentzians. These simple analytic functions consists of parameters $\Lambda^i$, which are defined as follows.
\begin{align} \label{eq:Lambda}
	\Lambda^i&=\lambda_{00}^i+\lambda_{10}^i\eta \nonumber \\
	&+(\chi_{\mathrm{PN}}-1)(\lambda_{01}^i+\lambda_{11}^i\eta+\lambda_{21}^i\eta^2) \nonumber \\ 
	&+(\chi_{\mathrm{PN}}-1)^2(\lambda_{02}^i+\lambda_{12}^i\eta+\lambda_{22}^i\eta^2) \nonumber \\
	&+(\chi_{\mathrm{PN}}-1)^3(\lambda_{03}^i+\lambda_{13}^i\eta+\lambda_{23}^i\eta^2)
\end{align}
$\Lambda^i$ depends on waveform coefficients $\lambda$ and intrinsic parameters including symmetric mass ratio $\eta$ and post-newtonian spin parameter $\chi_{\mathrm{PN}}$, 
\begin{align}
	\chi_{\mathrm{PN}}=\frac{m_1\chi_1+m_2\chi_2}{m_1+m_2}-\frac{38\eta}{113}(\chi_1+\chi_2).
\end{align}
Here, $m_{1,2}$ and $\chi_{1,2}$ are the mass and spin of larger and smaller black hole respectively. Finally, the individual segments are connected in a way that the final waveform is continuous in its first derivative.

From Eq. \ref{eq:Lambda}, we can see that the values of $\lambda$ are fundamental to waveform generation, which can significantly affect the shape of final waveforms. Thus, having a set of accurate waveform coefficients is important. Generally, waveform coefficients are obtained by calibrating with NR waveforms, which are waveforms computed using NR simulations. In the case of \citep{khan2016frequency}, $\lambda$ were obtained by fitting model-generated waveforms to NR waveforms. For each NR simulation, they can obtain one set of $\Lambda$'s through optimization. With many sets of $\Lambda$, $\lambda$ are subsequently found by fitting against Eq. \ref{eq:Lambda}. However, this piece-wise fitting deployed by \citep{khan2016frequency} causes calibrated coefficients to have systematic biases. Since coefficients were not fitted jointly, correlations between segments are omitted. Hence, the model introduces systematic biases to $\lambda$ and will be accumulated and passed along to the data analysis pipeline. Also, their calibration procedure does not guarantee to have the optimal set of $\lambda$, since the process of connecting segments alters the previously fitted waveform. The model-generated waveforms do not take this effect into account, and thus introduces additional inaccuracies.

@@

In the original calibration \citep{khan2016frequency,husa2016frequency}, training waveforms are hybrid waveforms of NR simulations and SpinAlignedEOB (SEOB) waveforms. The low frequency inspiral part is taken from the SEOB waveforms while the rest of the waveforms are taken from NR simulations. Instead, we solely use NR waveforms for comparison, since most NR waveforms used have long enough time series data, i.e.~$>15$ orbits \citep{boyle2019sxs}, in which they are long enough to contain part of the inspiral segment and all merger and ringdown frequency information. We take the frequency limits as $f_{\mathrm{min}}=0.1f_{\mathrm{RD}}$ and $f_{\mathrm{max}}=1.2f_{\mathrm{RD}}$, where $f_{\mathrm{RD}}$ is the frequency at ringdown. This range covers most of the IMRPhenomD's frequency range, except the minimum frequency is set higher than that in the original calibration due to NR length. When compared with IMRPhenomC, the frequency range is slightly extended to have a higher maximum frequency. \te{What is the frequency spacing?}

\te{I think this discussion needs to be much more precise. Having a waveform model calibrated to particular noise curve could make sense, but its inherently different to just fitting the phase and the amplitude separately like they do in the original paper. So I would recommend that our default is to use a flat PSD and then in addition discuss the one with the PSD. This way, I think we demonstrate more clearly that its the high dimensional fitting that helps, not the just changing the metric used when fitting.}
We choose to use two different noise spectra $S_n(f)$, namely the zero-detuned high-power (\zdethp) noise spectrum and a constant spectrum. Since in any data analysis tasks, model-generated waveforms will ultimately be used to compare with GW observations, they are subjected to the sensitivity of detectors. Hence, it is sensible to have waveforms calibrated with {\zdethp} spectrum rather than a non-weighted spectrum. However, with sensitivity curve involved, we have to choose a corresponding mass scale. Here, we simply choose $M=50M_{\odot}$ for all waveforms, since this mass scale is common in LIGO observations. On the other hand, we also recalibrated coefficients with the constant spectrum for a more general purpose.

@@

% \kw{Mention the main advantage in this study is we can optimize everything at once.}

% To recalibrate the model, we have to define loss functions that quantify the difference between the model-generated waveforms and NR waveforms. In the original calibration, they took the mean square error as the loss function for optimization. Instead, we directly use mismatch as our metric for loss functions. However, the mismatch of individual waveforms is not useful in optimization, since it does not represent all waveforms with various intrinsic parameters. We ought to calibrate coefficients that suit waveforms with different intrinsic parameters simultaneously, hence waveforms in different regions of parameter space should be used in the optimization scheme. Here, we chose two different loss functions to examine their ability to optimize the model, e.g. mean of individual mismatches $\mathcal{L}_{\mathrm{mean}}$ and fractional loss $\mathcal{L}_{\mathrm{fl}}$.

@@

% To recalibrate the model, we need to define a loss function that quantify ... We use mismatch over the set of all training waveforms as the loss function. We choose mismatch as the loss function because it is closely related to downstream objectives such as the likelihood in parameter estimation. The mismatch is averaged over the training dataset to cover the parameter space of interest. (used)
\begin{align}
	\mathcal{L}_{\mathrm{mean}}&=\frac{1}{N}\sum_{i=1}^N\mathcal{M}_i \\
	\mathcal{L}_{\mathrm{fl}}&=\frac{1}{N}\sum_{i=1}^N\frac{\mathcal{M}_i}{\mathcal{M}_{i,\mathrm{ini}}},
\end{align}	
$\mathcal{M}_i$ represents the mismatch of an individual training waveform, $\mathcal{M}_{i,\mathrm{ini}}$ represents the initial mismatch of the individual training waveform, and $N$ is the total number of individual training waveforms. For the first choice, it takes the mean of the mismatches, which serves as a basic loss function. However, it is prone to be dominated by a single waveform with a large mismatch. Other waveforms with smaller mismatches would be insignificant comparatively, and might not be able to improve under such optimization. Alternatively, the second choice, the mean of normalized mismatches, eliminates the aforementioned issue. Nevertheless, it excludes the information on initial mismatches. $\mathcal{L}_{\mathrm{fl}}$ restricts every training waveform to decrease at similar rates, hence it is hard to obtain optimized waveforms with mismatches in the same order of magnitude. Instead, their ratios in mismatches would remain approximately the same. Conversely, $\mathcal{L}_{\mathrm{mean}}$ allows the loss function to automatically adjust and final individual mismatches would be in a similar order of magnitude. In this paper, we display the results of using both loss functions and examine the difference between them.

@@

\te{I think we need a bit more discussion about the stopping criterion here. What is N, and why did we choose it to be this number? Ideally we would actually have a plot of the loss function during training. I don't have a good intuition for if its noisy. Does it plateau? If we wanted to ensure that people don't complain about overfitting we could also plot the loss of the validation set to show its not going up.}

@@

\begin{figure*}[t]
	\script{0154.py}
	\centering
	\includegraphics[width=\textwidth]{figures/0154.pdf}
	\caption{Comparison between original and optimized IMRPhenomD waveforms. Here shows the SXS:BBH:0154 NR waveform, which has mass ratio $q=1$ and $\chi_1=\chi_2=-0.8$. The original mismatch is around $2.8\times10^{-4}$ and the optimized mismatch is around $5.3\times10^{-5}$. Top: It shows the amplitude and phase of NR, original IMRPhenomD and optimized IMRPhenomD waveform. Bottom: It shows the relative error of amplitudes between NR and IMRPhenomD waveforms, and the absolute error of phases between NR and IMRPhenomD waveforms \te{I realize that this is also an error in the ripple paper, but the bottom panels should have abs round the whole y axis, otherwise why are they strictly positive? I actually think just plotting the error itself i.e. allowing for positive and negative values would potentially look better. Its also useful to add the vertical lines corresponding the different waveform regions. Otherwise one might think that the oscillations will line up with this and its some weird artifact of the splitting. The top and bottom panels should probably share x axes, or at least have the same scales so that they can be compared easily. }}
	\label{fig:0154}
\end{figure*}

@@

We first examine the effect of joint optimization on a single waveform. In Fig.~\ref{fig:0154}, we can see that the optimized waveform has better accuracy than the original waveform, especially in the inspiral region, where the amplitude has a $50\%$ decrease in error. We have chosen one of the testing waveforms listed in \citep{khan2016frequency} for a fair comparison. 
% In general, most waveforms within the neighborhood of the training waveforms show improvement in mismatches.

@@

% \kw{We then compute the mismatch for all testing waveforms and plot the distribution of the mismatch in figure X. We find the distribution...}

@@

% We believe that either the ansatz does not suit waveforms within certain regions of parameter space or the set of optimized coefficients falls to a minimum where they do not fit some testing waveforms. If in some region of parameter space, the ansatz does not fit well with NR waveforms, it would never be able to have consistent improvement under optimization. Instead, it would surf around the loss manifold with random fluctuations in mismatches. If the set of coefficients does not fit, then dividing the parameter space into regions and fitting separate sets of coefficients should give better results.

@@

Furthermore, we plot the parameter space of $\chi_1$ vs. $\chi_2$ in Fig.~\ref{fig:ps_q148}. Waveforms along the diagonal axis, i.e. $\chi_1\approx\chi_2$, show good mismatch improvements. We expect to see this feature since the original coefficients were fitted using NR waveforms with equal or similar spin, hence the model prefers waveforms with similar spin. One interesting feature is how the second and fourth quadrants respond to optimization. In the second quadrant ($\chi_1<0$ and $\chi_2>0$), waveforms generally improve with along optimization. However, mismatches in the fourth quadrant ($\chi_1>0$ and $\chi_2<0$) do not improve after optimization. Most waveforms even turned worse after optimization. These waveforms correspond to the waveforms in the high mismatch tail in Fig.~\ref{fig:q148}. \te{I think this kind of behaviour needs to be matched with the discussion about our stopping criteria. If it gets worse, why aren't we stopping earlier?}

% Waveform mismatches in the fourth quadrant, i.e. $\chi_1>0$ and $\chi_2<0$, performed worse after optimized. IMRPhenomD is constructed using single spin parameter, where there are degeneracy between $\chi_1$ and $\chi_2$. In regions with opposite extreme spin components, degeneracy significantly alters intrinsic parameters passed into waveform generation, hence the fourth quadrant shows such feature.

\begin{figure}[t]
	\script{ps_q148_qchi.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/ps_q148_qchi.pdf}
	\caption{Parameter space of testing waveforms of $q$~vs.~$\chi_{\mathrm{PN}}$. We use the recalibrated result from $\mathcal{L}_{\mathrm{mean}}$ with the constant noise spectrum and training waveforms in Tab.~\ref{tab:q148}. Here, the colorbar represents the $\log_{10}$ difference between optimized and original unweighted mismatches. \te{I find this plot a little odd. The bounding of between -1 and 1 gives the impression that the colourbar has strict limits between these regions. Are we truncating the colors?And if so, why?}}
	\label{fig:ps_q148_qchi}
\end{figure}
\begin{figure}[t]
	\script{ps_q148_chi1chi2.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/ps_q148_chi1chi2.pdf}
	\caption{Parameter space of testing waveforms of $\chi_1$~vs.~$\chi_2$. We use the recalibrated result from $\mathcal{L}_{\mathrm{mean}}$ with the constant noise spectrum and training waveforms in Tab.~\ref{tab:q148}.}
	\label{fig:ps_q148}
\end{figure}

@@

\begin{figure}[t]
	\script{all_quadrants.py}
	\centering
	\includegraphics[width=\columnwidth]{figures/all_quadrants.pdf}
	\caption{Distributions of mismatches after optimizing in separate quadrants. We use a constant noise spectrum to calculate mismatch and $\mathcal{L}_{\mathrm{mean}}$ for the loss function. Generally, most waveforms with mismatch $>10^{-2}$ lies in the fourth quadrant. \te{It would be nice to have four histograms for the four quadrants here. Ideally for both the original and optimized waveform but this might get a little cluttered. Maybe just plot the best and worst quadrant?}\te{This figure also doesn't appear to be referenced in the text?}}
	\label{fig:all_quadrants}
\end{figure}

@@

%\begin{enumerate}
%	\item Comparison with the original paper is not the same. (Different waveforms, different ways to modify the waveform, different range of frequencies)
%	\item More waveforms are taken so it should be more robust, since the parameter space coverage is better.
%    \item Problems with IMRPhenomD model, i.e. $\chi_{\mathrm{eff}}$ reduces the dimension of spin space $\chi_1, \chi_2$, so the model is flawed. Comparison issues. (Caveat)
%    \item Can in principle split parameter space into regions that can be separately optimized. If not, then its must be the model's problem. Would the region classification be made automatic. Are there any algorithms to do so?
%    \item Future work (Repeat on other GW models. Mapping between NR surrogate to see any systematics.)
%\end{enumerate}

We have shown the result of recalibrating waveform coefficients. One thing to note is that our recalibration procedure is not exactly the same as the original calibration. For instance, we use a different set of NR waveforms, frequency range, etc. Nonetheless, as the decrease in mismatch is rather significant, this optimization procedure should be able to improve the accuracy of IMRPhenomD on a similar scale regardless of the differences. Here, this result serves as a demonstration of the general method used.  
% In Fig.~\ref{fig:0154}, the error in the inspiral region is around halved for both amplitude and phase. Similarly, for the merger-ringdown region, the optimized waveforms also show great improvement.

@@

% Can we further check systematic bias by injection? But how can we know the real mass or spin in the first place if we disregard GW models.

@@

% From analyzing mismatches in parameter space, we investigated the accuracy of generated waveforms based on their mass ratio and spin. Similar studies can be performed on other GW models to give better criteria to

% Improved the IMRPhenomD model. Found regions that can be improved. Checked ansatz.
